Formal Modelling of a Microcontroller Instruction Set in B

### 2009-06-29 trunk/papers/SBMF2009/source/paper.tex
Novamente substitui microprocessor por microcontroller

Several iterations were needed to provide the good library definitions as well as
to fine-tune the model of the microprocessor instructions by factoring common
functionalities into auxiliary definitions.

>>>>

Several iterations were needed to provide the good library definitions as well as
to fine-tune the model of the microcontroller instructions by factoring common
functionalities into auxiliary definitions.
